Towards a framework for reasoning about stateful compiler IRs using coinductive reasoning.

### 2024-06-18 paper.tex
fix citations

@@

Now, formal verification has been done before. Most notable is the
CompCert project: a fully verified end-to-end C compiler.
{[}{[}@leroyCompCertFormallyVerified{]}{]} Yet, the vast majority of
code today is still being compiled with non-verified compilers. We ask,
thus, how do we formally verify not \emph{a} compiler, but, how do we
scale formal verification to \emph{mainstream} compilers.

Take, for example, LLVM, a widely-used open-source compiler that is used
to compile, e.g., C, C++, Fortran, Rust, and Swift. Verifying the entire
LLVM codebase, comprising of a few million lines of C++ code, is
infeasible. Instead, we follow the same approach as Lopez et al and
focus on verifying that individual rewrites on a compiler IR preserve
semantics. {[}{[}@lopesAlive2BoundedTranslation2021{]}{]}

@@

In the next two years, I'd like to look into a feature of MLIR called
\emph{Graph Regions}. Specific dialects may use such regions to allow a
variable to be used \emph{before} it is defined --- hence, turning the
def-use chain into a general graph. Generally, the semantics of such
dialects are statefull, and cycles are broken by looking at the value of
a variable at a previous state. For example, graph regions are used by
dialects that model hardware {[}{[}@eldridgeMLIRHardwareCompiler{]}{]},
where variables model wires and cycles represent physical cycles in the
circuit.

@@

\hypertarget{related-work}{%
\section{Related work}\label{related-work}}

@@

\hypertarget{verified-compilation}{%
\subsection{Verified Compilation}\label{verified-compilation}}

{[}{[}@leroyCompCertFormallyVerified\textbar CompCert{]}{]} is the
seminal work when it comes to verified compilation: an end-to-end
verified to not miscompile compiler for the C language. However, exactly
because it's an end-to-end verified monolith, CompCert is not
competitive compared to traditional non-verified compilers. Outside of
certain high-risk domains, where traditionally optimizations would be
turned off entirely {[}{[}@kastnerCompCertPracticalExperience{]}{]}, the
vast majority of C code is thus still compiled with non-verified
compilers, which studies have shown to be prone to miscompilations
{[}{[}@yangFindingUnderstandingBugs2011{]}{]}.

Lopes et al.~propose \emph{translation validation} as a way to scale
formal verification. {[}{[}@lopesAlive2BoundedTranslation2021{]}{]}
Their implementation, called Alive, has found wide adoption in the
development of LLVM. Given a declarative description of an optimization
as a source and target pattern in LLVM IR, the tool uses an SMT solver
to automatically determine whether the optimized pattern exhibits only
behaviours of the original program.

@@

Our group has been developing
{[}\protect\hyperlink{leanmlir}{LeanMLIR}{]}, a framework for giving
semantics to MLIR-style compiler IRs in the Lean theorem prover
{[}{[}@demouraLeanTheoremProver2015{]}{]}. As a theorem prover, Lean is
much more expressible than SMT solvers. Among theorem provers, Lean is
particularly suited for this purpose because of it's community of
mathematicians developing a comprehensive mathematical library
{[}{[}@themathlibcommunityLeanMathematicalLibrary2020{]}{]}, and because
of it's highly extensive syntax and meta-programming capabilities
{[}{[}@ullrichNotationsHygienicMacro2022{]}{]}{[}{[}@paulinoMetaprogrammingLean{]}{]}.

@@

\hypertarget{coinductive-types}{%
\subsection{Coinductive Types}\label{coinductive-types}}

@@

For us, the main difference of interest is that inductive datastructures
are finite, while coinductive datastructures capture infinite
behaviours.
{[}{[}@sangiorgiIntroductionBisimulationCoinduction2011{]}{]} In
particular, since Lean requires us to prove that recursive functions are
terminating, we need corecursion to correctly model things like infinite
loops and other non-terminating behaviours that are common in compiler
IRs.

For example, Xia et al.~used interaction trees, a coinductive type, in
their Coq formalization of recursive and impure programs.
{[}{[}@xiaInteractionTreesRepresenting2020{]}{]} Similarly, MLIR has an
``fsm'' dialect \footnote{https://circt.llvm.org/docs/Dialects/FSM/}
centred on finite state machines. Such automata are understood to be
coinductive in nature, so mechanizing the semanantics of this dialect in
Lean will likely require coinduction.

Consequently, we need a user-friendly way to define coinductive
structures and to formalize coinductive proof methods in Lean. Key prior
work in this area include my own master's thesis
{[}{[}@keizerImplementingDefinitionalCo{]}{]}, which is based on earlier
work by Avigad et al that models coinductive as quotients of polynomial
functors (QPFs){[}{[}@avigadDataTypesQuotients2019{]}{]}.

@@

When looking at coinductive types in other theorem provers, we
distinguish between languages like Isabelle
{[}{[}@traytelCategoryTheoryBased{]}{]}, which follow the same
coinduction-as-a-library approach, and languages like Coq
{[}{[}@gimenezTutorialRecursiveTypes1998{]}{]}{[}{[}@gimenezApplicationCoinductiveTypes1996{]}{]}
or Agda which have modified their trusted kernels to support
coinduction.

Isabelle, in particular, is relevant because it's construction of
coinductive types, in terms of \emph{bounded natural functors} is
closely related to our construction in terms of QPFs.
{[}{[}@furerQuotientsBoundedNatural2022{]}{]} There are still new
challenges, however, because Lean's dependent types mean we have to
worry about the distinction between definitional equality (which is a
decidable, but weaker notion of equality) and propositional equality
(which captures more things that are intuitively equal, but requires
proof). Isabelle, in contrast, uses a weaker logical system where all
equalities are decidable.

In contrast, the coinduction-in-the-kernel approach allows us to modify
the kernel to understand coinduction and ensure the kernel recognizes
the desired definitonal equalities. However, modifying the trusted
kernel carries a large burden of proof, since the changes could
compromise the logical soundness of the entire system. In fact, the
original implementation of coinduction, called \emph{positive}
coinduction, is nowadays discouraged in favour of an alternative
implementation, since positive coinduction breaks the subject reduction
property \footnote{ The subject reduction property states that reducing
  a program does not change its type}{[}{[}@sozeauCorrectCompleteType{]}{]}.
Our coinductives-as-a-library approach requires no new axioms nor
changes to the kernel, and is thus guaranteed not to change any meta
properties of Lean.

\hypertarget{progress-report}{%
\section{Progress Report}\label{progress-report}}

@@

\hypertarget{lean-mlir}{%
\subsection{Lean MLIR}\label{lean-mlir}}

@@

\hypertarget{bitvectors}{%
\subsection{Bitvectors}\label{bitvectors}}

@@

\hypertarget{future-plans}{%
\section{Future plans}\label{future-plans}}

\hypertarget{bitvectors-1}{%
\subsection{Bitvectors}\label{bitvectors-1}}

@@

As mentioned in the progress report, I'm currently contributing to a
verified bitblasting procedure in Lean, called LeanSAT. Once this is
implemented, I plan to write a paper contrasting this verified
bitblaster and SAT solver with popular non-verified SMT solvers like Z3,
to investigate what exactly the cost is of the extra assurance that a
verified implementation gives. This is particularly relevant, since,
just like compilers, SMT solvers are highly complicated pieces of
software in which bugs are known to exist
{[}{[}@brummayerFuzzingDeltadebuggingSMT2009{]}{]}.

\hypertarget{arbitrary-widths}{%
\subsubsection{Arbitrary widths}\label{arbitrary-widths}}

@@

\hypertarget{amazon-internship}{%
\subsubsection{Amazon Internship}\label{amazon-internship}}

@@

\hypertarget{coinduction}{%
\subsection{Coinduction}\label{coinduction}}

@@

\hypertarget{productivity-checking}{%
\subsubsection{Productivity Checking}\label{productivity-checking}}

@@

I will be a co-supervising an undergraduate student over the summer who
will be implementing support for corecursive functions using a
\emph{guarded} productivity checker. That is, this first implementation
will only allow only functions where each corecursive call occurs behind
a constructor. This check is known to incomplete, and more complicated
schemes have been studied
({[}{[}@blanchetteFriendsBenefitsImplementing2017{]}{]}), but a
guardedness easier to implement and will most likely be sufficient for
now --- the initial implementation of corecursion in Coq also allowed
only guarded corecursion {[}{[}@gimenezTutorialRecursiveTypes1998{]}{]}.
Of course, if there is still time left in the internship after this goal
has been reached, we will attempt to implement more complicated schemes
as well.

\hypertarget{runtime-behaviour}{%
\subsubsection{Runtime behaviour}\label{runtime-behaviour}}

\begin{quote}
Jan '25 - May '25
\end{quote}

@@

\hypertarget{leanmlir}{%
\subsection{LeanMLIR}\label{leanmlir}}

@@

\hypertarget{non-termination}{%
\subsubsection{Non-termination}\label{non-termination}}

@@

Therefore, I'd like to use my library for coinductive types to define a
coinductive monad which supports computable infinite behaviours, drawing
inspiration from the interaction tree library for coq.
{[}{[}@xiaInteractionTreesRepresenting2020{]}{]} This addresses a
weakness in LeanMLIR while simultaneously giving a nice case study for
the usability of the coinduction library.

\hypertarget{graph-regions-parametric-coinduction}{%
\subsubsection{Graph Regions \& Parametric
Coinduction}\label{graph-regions-parametric-coinduction}}

@@

Graph regions are thus inherently stateful, and modelling them is a
particularly good use-case for coinductive types and coinductive
reasoning. To facilitate easy verification of coinductive properties in
this setting, I would like to investigate supporting parametrized
coinductive proofs {[}{[}@hurPowerParameterizationCoinductive{]}{]} in
the coinductive types framework.

\hypertarget{stretch-goal-iris}{%
\subsection{Stretch Goal: Iris}\label{stretch-goal-iris}}

\begin{quote}
{[}!TODO{]} Talk about how denotational semantics are cool, and how the
aforementioned improvements will let us define dialects with
side-effects, but reasoning about them will still be a bit painful. We'd
really like to reason with program logics instead, in particular, iris:
{[}{[}@jungIrisMonoidsInvariants2015{]}{]}{[}{[}@jungHigherorderGhostState2016{]}{]}
\end{quote}

>>>>

\def\paperversiondraft{draft}
\def\paperversionnormal{normal}

% If the paper version is set to 'normal' mode keep it,
% otherwise set it to 'draft' mode.
\ifx\paperversion\paperversionnormal
\else
  \def\paperversion{draft}
\fi

\documentclass[a4paper]{scrartcl}

\usepackage{colortbl}

% 'draftonly' environment
\usepackage{environ}
\ifx\paperversion\paperversiondraft
\newenvironment{draftonly}{}{}
\else
\NewEnviron{draftonly}{}
\fi

% Most PL conferences are edited by conference-publishing.com. Follow their
% advice to add the following packages.
%
% The first enables the use of UTF-8 as character encoding, which is the
% standard nowadays. The second ensures the use of font encodings that support
% accented characters etc. (Why should I use this?). The mictotype package
% enables certain features 'to­wards ty­po­graph­i­cal per­fec­tion
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{microtype}

\usepackage{xargs}
\usepackage{lipsum}
\usepackage{xparse}
\usepackage{xifthen, xstring}
\usepackage{xspace}
\usepackage{marginnote}
\usepackage{etoolbox}
\usepackage[acronym,shortcuts]{glossaries}

\input{tex/setup.tex}
% \input{tex/acm.tex}

\usemintedstyle{colorful}

% Newer versions of minted require the 'customlexer' argument for custom lexers
% whereas older versions require the '-x' to be passed via the command line.
\makeatletter
\ifcsdef{minted@optlistcl@quote}
{
\newminted[mlir]{tools/MLIRLexer.py:MLIRLexerOnlyOps}{customlexer, mathescape}
\newminted[xdsl]{tools/MLIRLexer.py:MLIRLexer}{customlexer, mathescape, style=murphy}
\newminted[lean4]{tools/Lean4Lexer.py:Lean4Lexer}{customlexer, mathescape}
}
{
\newminted[mlir]{tools/MLIRLexer.py:MLIRLexerOnlyOps -x}{mathescape}
\newminted[xdsl]{tools/MLIRLexer.py:MLIRLexer -x}{mathescape, style=murphy}
\newminted[lean4]{tools/Lean4Lexer.py:Lean4Lexer -x}{mathescape}
}
\makeatother

% We use the following color scheme
% 
% This scheme is both print-friendly and colorblind safe for
% up to four colors (including the red tones makes it not
% colorblind safe any more)
%
% https://colorbrewer2.org/#type=qualitative&scheme=Paired&n=4

\definecolor{pairedNegOneLightGray}{HTML}{cacaca}
\definecolor{pairedNegTwoDarkGray}{HTML}{827b7b}
\definecolor{pairedOneLightBlue}{HTML}{a6cee3}
\definecolor{pairedTwoDarkBlue}{HTML}{1f78b4}
\definecolor{pairedThreeLightGreen}{HTML}{b2df8a}
\definecolor{pairedFourDarkGreen}{HTML}{33a02c}
\definecolor{pairedFiveLightRed}{HTML}{fb9a99}
\definecolor{pairedSixDarkRed}{HTML}{e31a1c}

\createtodoauthor{grosser}{pairedOneLightBlue}
\createtodoauthor{authorTwo}{pairedTwoDarkBlue}
\createtodoauthor{authorThree}{pairedThreeLightGreen}
\createtodoauthor{authorFour}{pairedFourDarkGreen}
\createtodoauthor{authorFive}{pairedFiveLightRed}
\createtodoauthor{authorSix}{pairedSixDarkRed}

\newacronym{ir}{IR}{Intermediate Representation}

\graphicspath{{./images/}}

% Define macros that are used in this paper
%
% We require all macros to end with a delimiter (by default {}) to enusure
% that LaTeX adds whitespace correctly.
\makeatletter
\newcommand\requiredelimiter[2][########]{%
  \ifdefined#2%
    \def\@temp{\def#2#1}%
    \expandafter\@temp\expandafter{#2}%
  \else
    \@latex@error{\noexpand#2undefined}\@ehc
  \fi
}
\@onlypreamble\requiredelimiter
\makeatother

\newcommand\newdelimitedcommand[2]{
\expandafter\newcommand\csname #1\endcsname{#2}
\expandafter\requiredelimiter
\csname #1 \endcsname
}

\newdelimitedcommand{leanmlir}{LeanMLIR}

\usepackage{booktabs}
\newcommand{\ra}[1]{\renewcommand{\arraystretch}{#1}}

\usepackage[verbose]{newunicodechar}
\newunicodechar{₁}{\ensuremath{_1}}
\newunicodechar{₂}{\ensuremath{_2}}
\newunicodechar{∀}{\ensuremath{\forall}}
\newunicodechar{α}{\ensuremath{\alpha}}
\newunicodechar{β}{\ensuremath{\beta}}

% \circled command to print a colored circle.
% \circled{1} pretty-prints "(1)"
% This is useful to refer to labels that are embedded within figures.
\DeclareRobustCommand{\circled}[2][]{%
    \ifthenelse{\isempty{#1}}%
        {\circledbase{pairedOneLightBlue}{#2}}%
        {\autoref{#1}: \hyperref[#1]{\circledbase{pairedOneLightBlue}{#2}}}%
}

% listings don't write "Listing" in autoref without this.
\providecommand*{\listingautorefname}{Listing}
\newcommand{\sectionautorefname}{Section}
\newcommand{\subsectionautorefname}{Section}
\newcommand{\subsubsectionautorefname}{Section}

\begin{document}

%% Title information
% \title{First Year Report}       %% [Short Title] is optional;
                                      %% when present, will be used in
                                      %% header instead of Full Title.
\title{Towards a framework for reasoning about stateful compiler IRs 
using coinductive reasoning.}                                      
\subtitle{First Year Report}

\author{Alex Keizer \small{(ack55)}}
\date{}

% \begin{abstract}
% % An abstract should consist of six main sentences:
% %  1. Introduction. In one sentence, what’s the topic?
% %  2. State the problem you tackle.
% %  3. Summarize (in one sentence) why nobody else has adequately answered the research question yet.
% %  4. Explain, in one sentence, how you tackled the research question.
% %  5. In one sentence, how did you go about doing the research that follows from your big idea.
% %  6. As a single sentence, what’s the key impact of your research?

% % (http://www.easterbrook.ca/steve/2010/01/how-to-write-a-scientific-abstract-in-six-easy-steps/)

% \end{abstract}
\maketitle

@@

Now, formal verification has been done before. Most notable is the
CompCert project: a fully verified end-to-end C compiler.~\cite{leroyCompCertFormallyVerified} Yet, the vast majority of
code today is still being compiled with non-verified compilers. We ask,
thus, how do we formally verify not \emph{a} compiler, but, how do we
scale formal verification to \emph{mainstream} compilers.

Take, for example, LLVM, a widely-used open-source compiler that is used
to compile, e.g., C, C++, Fortran, Rust, and Swift. Verifying the entire
LLVM codebase, comprising of a few million lines of C++ code, is
infeasible. Instead, we follow the same approach as Lopez et al and
focus on verifying that individual rewrites on a compiler IR preserve
semantics.~\cite{lopesAlive2BoundedTranslation2021}

@@

In the next two years, I'd like to look into a feature of MLIR called
\emph{Graph Regions}. Specific dialects may use such regions to allow a
variable to be used \emph{before} it is defined --- hence, turning the
def-use chain into a general graph. Generally, the semantics of such
dialects are statefull, and cycles are broken by looking at the value of
a variable at a previous state. For example, graph regions are used by
dialects that model hardware,
where variables model wires and cycles represent physical cycles in the
circuit.~\cite{eldridgeMLIRHardwareCompiler}

@@

\section{Related work}\label{related-work}

@@

\subsection{Verified Compilation}\label{verified-compilation}

CompCert is the
seminal work when it comes to verified compilation: an end-to-end
verified to not miscompile compiler for the C language. \cite{leroyCompCertFormallyVerified}
However, exactly
because it's an end-to-end verified monolith, CompCert is not
competitive compared to traditional non-verified compilers. Outside of
certain high-risk domains, where traditionally optimizations would be
turned off entirely \cite{kastnerCompCertPracticalExperience}, the
vast majority of C code is thus still compiled with non-verified
compilers, which studies have shown to be prone to miscompilations
\cite{yangFindingUnderstandingBugs2011}.

Lopes et al.~propose \emph{translation validation} as a way to scale
formal verification. \cite{lopesAlive2BoundedTranslation2021}
Their implementation, called Alive, has found wide adoption in the
development of LLVM. Given a declarative description of an optimization
as a source and target pattern in LLVM IR, the tool uses an SMT solver
to automatically determine whether the optimized pattern exhibits only
behaviours of the original program.

@@

Our group has been developing
LeanMLIR, a framework for giving
semantics to MLIR-style compiler IRs in the Lean theorem prover.~\cite{demouraLeanTheoremProver2015} As a theorem prover, Lean is
much more expressible than SMT solvers. Among theorem provers, Lean is
particularly suited for this purpose because of it's community of
mathematicians developing a comprehensive mathematical library,~\cite{themathlibcommunityLeanMathematicalLibrary2020} 
and because of it's highly extensive syntax and meta-programming capabilities~\cite{ullrichNotationsHygienicMacro2022, paulinoMetaprogrammingLean}.

@@

\subsection{Coinductive Types}\label{coinductive-types}

@@

For us, the main difference of interest is that inductive datastructures
are finite, while coinductive datastructures capture infinite
behaviours.
\cite{sangiorgiIntroductionBisimulationCoinduction2011} In
particular, since Lean requires us to prove that recursive functions are
terminating, we need corecursion to correctly model things like infinite
loops and other non-terminating behaviours that are common in compiler
IRs.

For example, Xia et al.~used interaction trees, a coinductive type, in
their Coq formalization of recursive and impure programs.
\cite{xiaInteractionTreesRepresenting2020} Similarly, MLIR has an
``fsm'' dialect \footnote{https://circt.llvm.org/docs/Dialects/FSM/}
centred on finite state machines. Such automata are understood to be
coinductive in nature, so mechanizing the semanantics of this dialect in
Lean will likely require coinduction.

Consequently, we need a user-friendly way to define coinductive
structures and to formalize coinductive proof methods in Lean. Key prior
work in this area include my own master's thesis
\cite{keizerImplementingDefinitionalCo}, which is based on earlier
work by Avigad et al that models coinductive as quotients of polynomial
functors (QPFs)\cite{avigadDataTypesQuotients2019}.

@@

When looking at coinductive types in other theorem provers, we
distinguish between languages like Isabelle
\cite{traytelCategoryTheoryBased}, which follow the same
coinduction-as-a-library approach, and languages like Coq
\cite{gimenezTutorialRecursiveTypes1998}\cite{gimenezApplicationCoinductiveTypes1996}
or Agda which have modified their trusted kernels to support
coinduction.

Isabelle, in particular, is relevant because it's construction of
coinductive types, in terms of \emph{bounded natural functors} is
closely related to our construction in terms of QPFs.
\cite{furerQuotientsBoundedNatural2022} There are still new
challenges, however, because Lean's dependent types mean we have to
worry about the distinction between definitional equality (which is a
decidable, but weaker notion of equality) and propositional equality
(which captures more things that are intuitively equal, but requires
proof). Isabelle, in contrast, uses a weaker logical system where all
equalities are decidable.

In contrast, the coinduction-in-the-kernel approach allows us to modify
the kernel to understand coinduction and ensure the kernel recognizes
the desired definitonal equalities. However, modifying the trusted
kernel carries a large burden of proof, since the changes could
compromise the logical soundness of the entire system. In fact, the
original implementation of coinduction, called \emph{positive}
coinduction, is nowadays discouraged in favour of an alternative
implementation, since positive coinduction breaks the subject reduction
property \footnote{ The subject reduction property states that reducing
  a program does not change its type}.~\cite{sozeauCorrectCompleteType}
Our coinductives-as-a-library approach requires no new axioms nor
changes to the kernel, and is thus guaranteed not to change any meta
properties of Lean.

\section{Progress Report}\label{progress-report}

@@

\subsection{Lean MLIR}\label{lean-mlir}

@@

\subsection{Bitvectors}\label{bitvectors}

@@

\section{Future plans}\label{future-plans}

\subsection{Bitvectors}\label{bitvectors-1}

@@

As mentioned in the progress report, I'm currently contributing to a
verified bitblasting procedure in Lean, called LeanSAT. Once this is
implemented, I plan to write a paper contrasting this verified
bitblaster and SAT solver with popular non-verified SMT solvers like Z3,
to investigate what exactly the cost is of the extra assurance that a
verified implementation gives. This is particularly relevant, since,
just like compilers, SMT solvers are highly complicated pieces of
software in which bugs are known to exist
\cite{brummayerFuzzingDeltadebuggingSMT2009}.

\subsubsection{Arbitrary widths}\label{arbitrary-widths}

@@

\subsubsection{Amazon Internship}\label{amazon-internship}

@@

\subsection{Coinduction}\label{coinduction}

@@

\subsubsection{Productivity Checking}\label{productivity-checking}

@@

I will be a co-supervising an undergraduate student over the summer who
will be implementing support for corecursive functions using a
\emph{guarded} productivity checker. That is, this first implementation
will only allow only functions where each corecursive call occurs behind
a constructor. This check is known to incomplete, and more complicated
schemes have been studied
(\cite{blanchetteFriendsBenefitsImplementing2017}), but a
guardedness easier to implement and will most likely be sufficient for
now --- the initial implementation of corecursion in Coq also allowed
only guarded corecursion \cite{gimenezTutorialRecursiveTypes1998}.
Of course, if there is still time left in the internship after this goal
has been reached, we will attempt to implement more complicated schemes
as well.

\subsubsection{Runtime behaviour}\label{runtime-behaviour}
\begin{quote}
Jan '25 - May '25
\end{quote}

@@

\subsection{LeanMLIR}\label{leanmlir}

@@

\subsubsection{Non-termination}\label{non-termination}

@@

Therefore, I'd like to use my library for coinductive types to define a
coinductive monad which supports computable infinite behaviours, drawing
inspiration from the interaction tree library for coq.
\cite{xiaInteractionTreesRepresenting2020} This addresses a
weakness in LeanMLIR while simultaneously giving a nice case study for
the usability of the coinduction library.

\subsubsection{Graph Regions \& Parametric
Coinduction}\label{graph-regions-parametric-coinduction}

@@

Graph regions are thus inherently stateful, and modelling them is a
particularly good use-case for coinductive types and coinductive
reasoning. To facilitate easy verification of coinductive properties in
this setting, I would like to investigate supporting parametrized
coinductive proofs~\cite{hurPowerParameterizationCoinductive} in
the coinductive types framework.

\subsection{Stretch Goal: Iris}\label{stretch-goal-iris}

\begin{quote}
{[}!TODO{]} Talk about how denotational semantics are cool, and how the
aforementioned improvements will let us define dialects with
side-effects, but reasoning about them will still be a bit painful. We'd
really like to reason with program logics instead, in particular, iris:
\cite{jungIrisMonoidsInvariants2015}\cite{jungHigherorderGhostState2016}
\end{quote}

% \input{y1review.tex}

% \begin{figure}
% % Link to figure
% %
% % https://docs.google.com/drawings/d/1juKp43D3rLC-luBQPwQZ_wCnDK2S_6C1k6USV0wKE0g/edit?usp=sharing
% \includegraphics[width=\columnwidth]{overview.pdf}
% \caption{Our key idea visualized}
% \grosser{Replace this figure with your own drawing.}
% \end{figure}

%% Bibliography
\bibliographystyle{plain}
\bibliography{references}

\end{document}
